CKY Parsing With Independence Constraints

### 2015-07-03 paper.tex
Finish tweaking tables (hopefully)

\begin{tabular}{lllllr}
Parser & Time (s) & Speedup & \# Binary Edges & F$_{\text{1}}$ & Parse Failures\\
\hline
baseline & 1558 & - & 1.75\texttimes{}10$^{\text{10}}$ (100\%) & 85.85 & 0\\
linear & 1283 (+100) & 1.21\texttimes{} (1.12\texttimes{}) & 1.08\texttimes{}10$^{\text{10}}$ (62\%) & 83.71 (-2.14) & 15\\
poly & 1106 (+2h) & 1.41\texttimes{} (.19\texttimes{}) & 9.74\texttimes{}10$^{\text{09}}$ (56\%) & 84.85 (-1.00) & 6\\
oracle & 1016 & 1.53\texttimes{} & 8.47\texttimes{}10$^{\text{09}}$ (48\%) & 86.71 (+0.86) & 4\\
\end{tabular}

@@

\begin{center}
\begin{tabular}{lrlrr}
Parser & Time (s) &  & F$_{\text{1}}$ & \\
\hline
baseline & 1538 &  & 85.54 & 0.00\\
linear & 1106 & 1.39\texttimes{} & 83.55 & -1.99\\
(w/ class.) & (1206) & (1.28\texttimes{}) &  & \\
poly & 1040 & 1.48\texttimes{} & 84.57 & -0.97\\
\end{tabular}
\end{center}

@@

\begin{tabular}{lrlrllr}
Classifier & MinSentLen & Constraints & Time (s) & \# Edges & F$_{\text{1}}$ & Parse Failures\\
\hline
- & - & baseline & 1558 & 1.75\texttimes{}10$^{\text{10}}$ (100\%) & 85.85 & 0\\
\hline
linear & 0 & default & 1283 & 1.08\texttimes{}10$^{\text{10}}$ (62\%) & 83.71 (-2.14) & 15\\
linear & 0 & precision & 1143 & 1.13\texttimes{}10$^{\text{10}}$ (65\%) & 84.05 (-1.80) & 7\\
linear & 0 & max precision & 1384 & 1.42\texttimes{}10$^{\text{10}}$ (81\%) & 85.55 (-0.30) & 2\\
linear & 0 & recall & 1024 & 7.80\texttimes{}10$^{\text{09}}$ (45\%) & 78.74 (-7.11) & 136\\
linear & 20 & default & 1126 & 1.12\texttimes{}10$^{\text{10}}$ (64\%) & 84.17 (-1.68) & 9\\
linear & 20 & precision & 1313 & 1.16\texttimes{}10$^{\text{10}}$ (66\%) & 84.43 (-1.42) & 4\\
linear & 20 & max precision & 1338 & 1.44\texttimes{}10$^{\text{10}}$ (82\%) & 85.59 (-0.26) & 2\\
linear & 20 & recall & 1121 & 8.24\texttimes{}10$^{\text{09}}$ (47\%) & 80.38 (-5.47) & 103\\
linear & 30 & default & 1312 & 1.28\texttimes{}10$^{\text{10}}$ (73\%) & 84.82 (-1.03) & 3\\
linear & 30 & precision & 1279 & 1.31\texttimes{}10$^{\text{10}}$ (75\%) & 85.01 (-0.84) & 1\\
linear & 30 & max precision & 1485 & 1.53\texttimes{}10$^{\text{10}}$ (87\%) & 85.63 (-0.22) & 1\\
linear & 30 & recall & 1140 & 1.02\texttimes{}10$^{\text{10}}$ (58\%) & 82.79 (-3.06) & 57\\
linear & 40 & default & 1476 & 1.51\texttimes{}10$^{\text{10}}$ (86\%) & 85.56 (-0.29) & 1\\
linear & 40 & precision & 1390 & 1.52\texttimes{}10$^{\text{10}}$ (87\%) & 85.59 (-0.26) & 0\\
linear & 40 & max precision & 1513 & 1.65\texttimes{}10$^{\text{10}}$ (94\%) & 85.75 (-0.10) & 0\\
linear & 40 & recall & 1403 & 1.33\texttimes{}10$^{\text{10}}$ (76\%) & 84.65 (-1.20) & 14\\
\hline
poly & 0 & default & 1106 & 9.74\texttimes{}10$^{\text{09}}$ (56\%) & 84.85 (-1.00) & 6\\
poly & 0 & precision & 1118 & 9.84\texttimes{}10$^{\text{09}}$ (56\%) & 85.12 (-0.73) & 4\\
poly & 0 & max precision & 1137 & \textbf{1.02\texttimes{}10$^{\text{10}}$ (58\%)} & \textbf{85.42 (-0.43)} & 2\\
poly & 0 & recall & 1050 & 9.25\texttimes{}10$^{\text{09}}$ (53\%) & 84.05 (-1.80) & 33\\
poly & 20 & default & 1070 & 1.02\texttimes{}10$^{\text{10}}$ (58\%) & 85.08 (-0.77) & 5\\
poly & 20 & precision & 1172 & 1.03\texttimes{}10$^{\text{10}}$ (59\%) & 85.25 (-0.60) & 3\\
poly & 20 & max precision & 1092 & 1.06\texttimes{}10$^{\text{10}}$ (61\%) & 85.41 (-0.44) & 2\\
poly & 20 & recall & 1088 & 9.68\texttimes{}10$^{\text{09}}$ (55\%) & 84.75 (-1.10) & 7\\
poly & 30 & default & 1222 & 1.20\texttimes{}10$^{\text{10}}$ (69\%) & 85.57 (-0.28) & 1\\
poly & 30 & precision & 1267 & 1.20\texttimes{}10$^{\text{10}}$ (69\%) & 85.62 (-0.23) & 1\\
poly & 30 & max precision & 1238 & 1.23\texttimes{}10$^{\text{10}}$ (70\%) & 85.65 (-0.20) & 1\\
poly & 30 & recall & 1238 & 1.16\texttimes{}10$^{\text{10}}$ (66\%) & 85.44 (-0.41) & 2\\
poly & 40 & default & 1465 & 1.49\texttimes{}10$^{\text{10}}$ (85\%) & 85.72 (-0.13) & 0\\
poly & 40 & precision & 1353 & 1.49\texttimes{}10$^{\text{10}}$ (85\%) & 85.75 (-0.10) & 0\\
poly & 40 & max precision & 1570 & 1.50\texttimes{}10$^{\text{10}}$ (86\%) & 85.78 (-0.07) & 0\\
poly & 40 & recall & 1489 & 1.47\texttimes{}10$^{\text{10}}$ (84\%) & 85.69 (-0.16) & 1\\
\hline
\end{tabular}

>>>>

\begin{tabular}{lllllr}
{\bf Parser} & {\bf Time (s)} & {\bf Speedup} & {\bf \# Binary Edges} & {\bf F$_{\text{1}}$} & {\bf Parse Failures}\\
\hline
baseline & 1558 & - & 1.75\texttimes{}10$^{\text{10}}$ (100\%) & 85.85 & 0\\
linear & 1283 (+100) & 1.21\texttimes{} (1.12\texttimes{}) & 1.08\texttimes{}10$^{\text{10}}$ (62\%) & 83.71 (-2.14) & 15\\
poly & 1106 (+2h) & 1.41\texttimes{} (.19\texttimes{}) & 9.74\texttimes{}10$^{\text{09}}$ (56\%) & 84.85 (-1.00) & 6\\
oracle & 1016 & 1.53\texttimes{} & 8.47\texttimes{}10$^{\text{09}}$ (48\%) & 86.71 (+0.86) & 4\\
\end{tabular}

@@

\begin{center}
\begin{tabular}{llll}
{\bf Parser} & {\bf Time} (s) & {\bf Speedup} & {\bf F$_{\text{1}}$} \\
%\hline
baseline & 1538 & & 85.54 \\
linear & 1106 & 1.39\texttimes{} & 83.55 (-1.99)\\
 & (+100) & (1.28\texttimes{}) &  \\
poly & 1040 & 1.48\texttimes{} & 84.57 (-0.97)\\
\end{tabular}
\end{center}

@@

\begin{tabular}{lrlrllr}
{\bf Classifier} & {\bf MinSentLen} & {\bf Constraints} & {\bf Time (s)} & {\bf \# Edges} & {\bf F$_{\text{1}}$} & {\bf Parse Failures}\\
\hline
- & - & baseline & 1558 & 1.75\texttimes{}10$^{\text{10}}$ (100\%) & 85.85 & 0\\
\hline
linear & 0 & default & 1283 & 1.08\texttimes{}10$^{\text{10}}$ (62\%) & 83.71 (-2.14) & 15\\
linear & 0 & precision & 1143 & 1.13\texttimes{}10$^{\text{10}}$ (65\%) & 84.05 (-1.80) & 7\\
linear & 0 & max precision & 1384 & 1.42\texttimes{}10$^{\text{10}}$ (81\%) & 85.55 (-0.30) & 2\\
linear & 0 & recall & 1024 & 7.80\texttimes{}10$^{\text{09}}$ (45\%) & 78.74 (-7.11) & 136\\
linear & 20 & default & 1126 & 1.12\texttimes{}10$^{\text{10}}$ (64\%) & 84.17 (-1.68) & 9\\
linear & 20 & precision & 1313 & 1.16\texttimes{}10$^{\text{10}}$ (66\%) & 84.43 (-1.42) & 4\\
linear & 20 & max precision & 1338 & 1.44\texttimes{}10$^{\text{10}}$ (82\%) & 85.59 (-0.26) & 2\\
linear & 20 & recall & 1121 & 8.24\texttimes{}10$^{\text{09}}$ (47\%) & 80.38 (-5.47) & 103\\
linear & 30 & default & 1312 & 1.28\texttimes{}10$^{\text{10}}$ (73\%) & 84.82 (-1.03) & 3\\
linear & 30 & precision & 1279 & 1.31\texttimes{}10$^{\text{10}}$ (75\%) & 85.01 (-0.84) & 1\\
linear & 30 & max precision & 1485 & 1.53\texttimes{}10$^{\text{10}}$ (87\%) & 85.63 (-0.22) & 1\\
linear & 30 & recall & 1140 & 1.02\texttimes{}10$^{\text{10}}$ (58\%) & 82.79 (-3.06) & 57\\
linear & 40 & default & 1476 & 1.51\texttimes{}10$^{\text{10}}$ (86\%) & 85.56 (-0.29) & 1\\
linear & 40 & precision & 1390 & 1.52\texttimes{}10$^{\text{10}}$ (87\%) & 85.59 (-0.26) & 0\\
linear & 40 & max precision & 1513 & 1.65\texttimes{}10$^{\text{10}}$ (94\%) & 85.75 (-0.10) & 0\\
linear & 40 & recall & 1403 & 1.33\texttimes{}10$^{\text{10}}$ (76\%) & 84.65 (-1.20) & 14\\
\hline
poly & 0 & default & 1106 & 9.74\texttimes{}10$^{\text{09}}$ (56\%) & 84.85 (-1.00) & 6\\
poly & 0 & precision & 1118 & 9.84\texttimes{}10$^{\text{09}}$ (56\%) & 85.12 (-0.73) & 4\\
poly & 0 & max precision & 1137 & \textbf{1.02\texttimes{}10$^{\text{10}}$ (58\%)} & \textbf{85.42 (-0.43)} & 2\\
poly & 0 & recall & 1050 & 9.25\texttimes{}10$^{\text{09}}$ (53\%) & 84.05 (-1.80) & 33\\
poly & 20 & default & 1070 & 1.02\texttimes{}10$^{\text{10}}$ (58\%) & 85.08 (-0.77) & 5\\
poly & 20 & precision & 1172 & 1.03\texttimes{}10$^{\text{10}}$ (59\%) & 85.25 (-0.60) & 3\\
poly & 20 & max precision & 1092 & 1.06\texttimes{}10$^{\text{10}}$ (61\%) & 85.41 (-0.44) & 2\\
poly & 20 & recall & 1088 & 9.68\texttimes{}10$^{\text{09}}$ (55\%) & 84.75 (-1.10) & 7\\
poly & 30 & default & 1222 & 1.20\texttimes{}10$^{\text{10}}$ (69\%) & 85.57 (-0.28) & 1\\
poly & 30 & precision & 1267 & 1.20\texttimes{}10$^{\text{10}}$ (69\%) & 85.62 (-0.23) & 1\\
poly & 30 & max precision & 1238 & 1.23\texttimes{}10$^{\text{10}}$ (70\%) & 85.65 (-0.20) & 1\\
poly & 30 & recall & 1238 & 1.16\texttimes{}10$^{\text{10}}$ (66\%) & 85.44 (-0.41) & 2\\
poly & 40 & default & 1465 & 1.49\texttimes{}10$^{\text{10}}$ (85\%) & 85.72 (-0.13) & 0\\
poly & 40 & precision & 1353 & 1.49\texttimes{}10$^{\text{10}}$ (85\%) & 85.75 (-0.10) & 0\\
poly & 40 & max precision & 1570 & 1.50\texttimes{}10$^{\text{10}}$ (86\%) & 85.78 (-0.07) & 0\\
poly & 40 & recall & 1489 & 1.47\texttimes{}10$^{\text{10}}$ (84\%) & 85.69 (-0.16) & 1\\
%\hline
\end{tabular}
